\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.55in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{xcolor}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlist[itemize]{leftmargin=1.2em, itemsep=2pt, topsep=2pt, parsep=0pt, partopsep=0pt}
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{8pt}{4pt}
\newcommand{\entry}[4]{
  \textbf{#1} \hfill #2\\
  #3 \hfill \textit{#4}
}
\newcommand{\paper}[4]{
  #1\\
  #2\\
  \textit{#3}\\
  #4
}

\begin{document}

\begin{center}
    {\LARGE \textbf{Sisi He}}\\
    \vspace{2pt}
    \href{mailto:sisihe914@gmail.com}{sisihe914@gmail.com} \quad
    \href{https://sisi-he.github.io/}{sisi-he.github.io} \quad
    \href{https://scholar.google.com/citations?user=iBPi1LYAAAAJ\&hl=zh-CN}{Google Scholar} \quad
    \href{https://www.linkedin.com/in/\%E6\%80\%9D\%E6\%80\%9D-\%E4\%BD\%95-308819419/}{LinkedIn}
    \vspace{2pt}\\
    \textit{Research Interests: Human--AI Collaboration $\cdot$ AI Agents $\cdot$ Embodied AI $\cdot$ Multimodal Interaction}
\end{center}

\section{Research Summary}
I study how AI agents can collaborate with people during open-ended physical activities. My research integrates multimodal perception, embodied interaction, and AI agents to build systems that understand human activities and provide adaptive assistance during complex real-world tasks such as repair and learning. More broadly, I am interested in AI systems that maintain shared context with people throughout long-term embodied collaboration.

\section{Education}
\entry{Nanyang Institute of Technology}{Jun 2022 -- Jun 2026}
{B.Eng. in Virtual Reality Technology; average score: 90.76/100; ranked 1st/56 (top 2\%)}{Nanyang, China}

\section{Publications}

\paper{\href{https://doi.org/10.1145/3772318.3790494}{\textbf{AI-Generated AR Reassembly Guidance from Disassembly Videos to Scaffold Everyday Repair}}}
{Wenjing Deng, Zhihao Yao, Xinhui Kang, Qirui Sun, Xintong Wu, \textbf{Sisi He}, Chenzhuo Xiang, Haipeng Mi}
{CHI 2026}
{\textbf{Contribution:} Primary technical contributor; designed and implemented the AR interaction system.}
\vspace{4pt}

\paper{\href{https://doi.org/10.1145/3746058.3758436}{\textbf{AI Extraction of Disassembly Videos for Generating AR Repair Instructions}}}
{Wenjing Deng, \textbf{Sisi He}, Xintong Wu, Y. Wan, Chenzhuo Xiang, Zhihao Yao, Haipeng Mi}
{UIST 2025 (Poster)}
{\textbf{Contribution:} Primary technical contributor; designed the AR interaction pipeline and co-developed the multi-agent AI framework. Received \textbf{Special Recognition for Sustainability in Posters}.}
\vspace{4pt}

\paper{\href{https://doi.org/10.1145/3772363.3798775}{\textbf{ReFashionPal: Exploring AI Assistant Embedded in How-to Videos to Support Garment Repurposing}}}
{Wenjing Deng, Shuzi Yin, Danqi Huang, \textbf{Sisi He}, Haipeng Mi}
{CHI EA 2026}
{\textbf{Contribution:} Primary technical contributor; designed and implemented the interaction system and LLM-based assistance pipeline.}

\section{Research Experience}

\entry{Multimodal AI for Material Culture Reconstruction}{Jul 2026 -- Present}
{Research Project}{}
\begin{itemize}
    \item Investigates how multimodal AI can interpret human activity, memory, and material environments from oral histories and historical photographs.
    \item Uses YOLO-World to detect and identify domestic objects in historical photographs as visual evidence for material culture reconstruction.
    \item Explores how object-level visual evidence can be integrated with oral narratives to reconstruct relationships between people, domestic objects, and lived experiences.
\end{itemize}

\entry{Future Lab, Tsinghua University}{Apr 2025 -- Sep 2025}
{Research Intern (AR Systems)}{Beijing, China}
\begin{itemize}
    \item Investigated whether procedural knowledge extracted from disassembly videos can replace manually authored AR repair instructions.
    \item Designed and implemented an AR guidance system that enables procedural repair assistance generated directly from disassembly videos.
    \item Evaluated the generated AR guidance through iterative system design and user studies.
\end{itemize}

\entry{Hong Kong University of Science and Technology (Guangzhou)}{Sep 2025 -- Feb 2026}
{Research Assistant}{Guangzhou, China}
\begin{itemize}
    \item Investigated how embodied motion interaction influences engagement in XR experiences.
    \item Led the development of a Kinect V2-based motion-sensing XR interactive system for embodied interaction and physical user engagement.
    \item Designed and conducted user studies to evaluate interaction flow, motion-sensing behavior, and participant experience.
\end{itemize}

\section{Industry and Development Experience}

\entry{Muyan Zhiyu Technology}{Feb 2026 -- Present}
{Unity Development Intern}{Beijing, China}
\begin{itemize}
    \item Designed a real-time multi-agent conversational framework for interactive game characters, connecting LLM-driven dialogue with character behavior logic.
    \item Implemented Unity-based interaction frameworks supporting responsive LLM-driven character behavior under real-time constraints.
\end{itemize}

\entry{Weidu Zhijian Technology}{May 2024 -- Aug 2024}
{VR Development Intern}{Beijing, China}
\begin{itemize}
    \item Optimized VR interaction logic and implemented immersive interaction features for Meta/Oculus-based applications.
    \item Built custom shaders, integrated Oculus haptic feedback, and connected application features with Meta Store APIs.
\end{itemize}

\section{Selected Honors and Awards}
\begin{itemize}
    \item UIST 2025 Special Recognition for Sustainability in Posters, 2025.
    \item National Inspirational Scholarship, 2025 and 2024.
    \item 1st Prize, 18th Advanced Robotics and Simulation Competition, National Finals (DF1), 2025.
    \item 1st Prize, National College Innovation and Entrepreneurship Competition, 2024.
    \item 2nd Prize, National College Student Computer Ability Competition, 2024.
    \item 2nd Prize, Provincial ``Challenge Cup'', 2023.
\end{itemize}

\section{Skills}
\textbf{Research Methods:} Human--AI interaction design, embodied interaction prototyping, AR/XR system design, user study design, qualitative and quantitative analysis.\\
\textbf{AI and Systems:} LLM agents, multimodal AI, object detection, procedural knowledge extraction.\\
\textbf{Programming:} Python, C\#, C/C++.\\

\end{document}
